Lightweight Scheduling for the PRAGMA Cloud Testbed

### 2016-07-14 paper.tex
Fix to get paper to build
Added a few more refs and few small grammar changes

\runningheads{A demonstration of the \journalabb\class file}

@@

% Decide to capitalize first word since http://www.quickanddirtytips.com/education/grammar/formatting-vertical-lists?page=2 indicates it's easier to capitalize
\textbf{Pragma\_boot:}  Rather than require a single cloud system at all sites, PRAGMA encourages sites to  deploy any virtualization technology that best fits their expertise. However, enabling a virtual cluster to be ported to different cloud hosting environments is a complex problem and requires tooling to retain the cluster relationship between head and worker nodes as well as software configurations.  In 2013, three pilot sites (UCSD, AIST, NCHC) developed a script to automate virtual cluster porting and demonstrated the same virtual cluster image being booted in three different cloud hosting environments, including Rocks/Xen, OpenNebula/KVM, and Amazon EC2.  Based on these experiences, the original prototype was redesigned and reimplemented as a \textit{pragma\_boot} toolkit with "drivers" to support  Rocks and OpenNebula.  In 2014, a feature was added to pragma\_boot to download and boot virtual cluster images from Amazon CloudFront~\cite{cloudfront}.

\textbf{Personal Cloud Controller:}  To provide researchers with an easy-to-use interface for managing the life cycle of their virtual clusters, a Personal Cloud Controller (PCC)  was started in 2014. This lightweight tool was designed to manage startup, status monitoring, and shutdown of a virtual cluster and was built on top of pragma\_boot and a well-known resource and workload management system HTCondor~\cite{condor}.   PCC also provided an option to create a multi-site virtual cluster leveraging an open-source virtual network overlay software IPOP~\cite{ipop} for creating its private network.

@@

Booked~\cite{booked} from Twinkle Toes software seemed the best suited to our needs compared to all the calendar reservation systems we evaluated.  It was easy to setup, had  a good look and feel, and was customizable.  It also had some nice additional features like usage reporting, a REST API interface, LDAP and Active Directory support, fine grained roles and permissions management, and user and group quotas.  After working with Booked during our pilot setup, we did find some weaknesses.  First, the documentation was very sparse and any needed PHP changes were time consuming due to its heavily object-oriented structure (for example, we had to go through many source code files to find the right place to change  or add functionality).   Second, the reservation frequency of the event is currently limited to one hour.  Based on today's PRAGMA needs this is sufficient because the time it takes to start up the virtual cluster 
is in the order of tens of minutes and  the user reservation is expected to be in the order of days. In the future when the virtual cluster startup  time shortens to minutes, the reservation frequency granularity can be optimized in order to avoid a potential of the underutilized resources.

@@

\begin{enumerate}
\item A user does a general search for available resources based on the number of CPUs, memory size, and networking configuration (e.g., IPOP, ViNE~\cite{vine}, or PRAGMA-ENT) that is needed.  
\item Available resources that fit the criteria are displayed to the user and their availability is shown in a calendar layout.  
\item The user selects the desired resources, the timeframe, virtual cluster image, and configuration details and submits them to the Cloud scheduler.  Once the reservation is verified and confirmed, the user will get an email confirmation.  
\item When the reservation is ready to be activated, the cloud scheduler will use PCC and pragma\_boot to launch the virtual cluster, automatically configure the private and public network configuration on the virtual cluster nodes, and email the user when the reconfigured cluster is ready.   
\end{enumerate}

@@

In our pilot implementation of the cloud scheduler, we made a number of simplifying assumptions to the design more comprehensible.

>>>>

%\runningheads{A demonstration of the \journalabb\class file}

@@

% Decide to capitalize first word since http://www.quickanddirtytips.com/education/grammar/formatting-vertical-lists?page=2 indicates it's easier to capitalize
\textbf{Pragma\_boot:}  Rather than require a single cloud system at all sites, PRAGMA encourages sites to  deploy any virtualization technology that best fits their expertise. However, enabling a virtual cluster to be ported to different cloud hosting environments is a complex problem and requires tooling to retain the cluster relationship between head and worker nodes as well as software configurations.  In 2013, three pilot sites (UCSD, AIST, NCHC) developed a script to automate virtual cluster porting and demonstrated the same virtual cluster image being booted in three different cloud hosting environments, including Rocks/Xen, OpenNebula/KVM, and Amazon EC2.  Based on these experiences, the original prototype was redesigned and reimplemented as a \textit{pragma\_boot} toolkit with "drivers" to support  Rocks and OpenNebula~\cite{pragmaboot}.  In 2014, a feature was added to pragma\_boot to download and boot virtual cluster images from Amazon CloudFront~\cite{cloudfront}.

\textbf{Personal Cloud Controller:}  To provide researchers with an easy-to-use interface for managing the life cycle of their virtual clusters, a Personal Cloud Controller (PCC)  was started in 2014~\cite{pcc}. This lightweight tool was designed to manage startup, status monitoring, and shutdown of a virtual cluster and was built on top of pragma\_boot and a well-known resource and workload management system HTCondor~\cite{condor}.   PCC also provided an option to create a multi-site virtual cluster leveraging an open-source virtual network overlay software IPOP~\cite{ipop} for creating its private network.

@@

Booked~\cite{booked} from Twinkle Toes software seemed the best suited to our needs compared to all the calendar reservation systems we evaluated.  It was easy to setup, had  a good look and feel, and was customizable.  It also had some nice additional features like usage reporting, a REST API interface, LDAP and Active Directory support, fine grained roles and permissions management, and user and group quotas.  After working with Booked during our pilot setup, we did find some weaknesses.  First, the documentation was very sparse and any needed PHP changes were time consuming due to its heavily object-oriented structure.  For example, we had to go through many source code files to find the right place to change  or add functionality.   Second, the reservation frequency of the event is currently limited to one hour.  Based on today's PRAGMA needs this is sufficient because the time it takes to start up the virtual cluster 
is in the order of tens of minutes and  the user reservation is expected to be in the order of days. In the future when the virtual cluster startup  time shortens to minutes, the reservation frequency granularity can be optimized in order to avoid a potential of the underutilized resources.

@@

\begin{enumerate}
\item A user does a general search for available resources based on the number of CPUs, memory size, and networking configuration (e.g., IPOP, ViNE~\cite{vine}, or PRAGMA-ENT) that is needed.  
\item Available resources that fit the criteria are displayed to the user and their availability is shown in a calendar layout.  
\item The user selects the desired resources, the timeframe, virtual cluster image, and configuration details and submits them to the Cloud scheduler.  Once the reservation is verified and confirmed, the user will get an email confirmation.  In the event two users try to reserve the same resources at the same time,
\item When the reservation is ready to be activated, the cloud scheduler will use PCC and pragma\_boot to launch the virtual cluster, automatically configure the private and public network configuration on the virtual cluster nodes, and email the user when the reconfigured cluster is ready.   
\end{enumerate}

@@

In our pilot implementation of the cloud scheduler, we made a number of simplifying assumptions to the design.
